\documentclass{beamer}
\usetheme{Hannover}
\usecolortheme{dolphin}

\title{Final Project}
\author{Zac Branson
\and Jay Kaiser
\and Mike Czerniakowski}


\begin{document}
%----------------------------------------------------------------
\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}
%----------------------------------------------------------------
%Presentation Slides
%----------------------------------------------------------------
\section{Introduction}
	\begin{frame}{Introduction}
		\begin{block}{Classifier}
			\begin{itemize}
		\item We are using TIMBL because:
		\item It lets us feed it strings: this makes maintaining word order of the immediate contexts much easier.
		\item We expect a memory based classifier to perform well for this task because: why?
			\end{itemize}
		\end{block}
	\end{frame}

\section{Plan}
	\begin{frame}{Preprocessing}
		\begin{block}{Bare Words}
			\begin{itemize}
		\item Remove all punctuation that doesn't indicate the end of a sentence (i.e. everything but ". ? !")
		\item make all capital letters lowercase
			\end{itemize}
		\end{block}	
		\begin{block}{Lemmas}
			\begin{itemize}
		\item Do the same as above but:
		\item Use NLTK's Romanian lemmatizer to lemmatize all words.
		\item Given that Romanian is a highly inflectional language, this might have a profound effect (good and/or bad).
		\item Good: greatly reduces sparsity of many words.  Bad: some of those suffixes might have been useful (case?, number?)
		\item We'll test that empirically.
			\end{itemize}
		\end{block}
	\end{frame}
	
	\begin{frame}{Features}
		\begin{block}{bare Words and Lemmas}
			\begin{itemize}
			\item Same context features from HW3: add here (lemmas instead of plain words in the case of lemmas)
			\item Second task is to incorporate PoS features: add tags of the same context words as independent features
			\item Possibly try it with just PoS tags and no words 
			\end{itemize}
		\end{block}
		\begin{block}{PoS Tags}
			\begin{itemize}
			\item add tags of the context words as independent features
			\item possibly try it with just PoS tags and no words 
			\item possibly try it with lemmas instead of words
			\end{itemize}
		\end{block}
	\end{frame}
	
	\begin{frame}{Parameters}
		\begin{block}{TIMBL Options}
			\begin{itemize}
			\item Use a bash script to brute force parameter optimization
			\item We optimize these parameters:  insert 
			\end{itemize}
		\end{block}
	\end{frame}
	
	\begin{frame}{Adding Unlabeled Data}
		\begin{block}{Bootstrapping Approach}
			\begin{itemize}
			\item TIMBL outputs distances, which can be used as a measure of prediction confidence
			\item Take the smallest n/10 of distances per class, add them to the training data, retrain the model
			\item Iterate:adding the next n/10 smallest distances, potentially until there are none left.  
			\item Profit.
			\end{itemize}
		\end{block}
	\end{frame}
	
	\begin{frame}{Preliminary Results}
		\begin{block}{Bare Words}
			table of results
		\end{block}
		\begin{block}{Lemmas}
			table of results
		\end{block}
		\begin{block}{Words + PoS Tags}
			table of results
		\end{block}
	\end{frame}
	
\end{document}